Describing demographic models is hard

### 2020-05-20 paper.tex
header and title thoughts

\aprcomment{title suggestions:\\
}

@@

\section{A missing parameter (or) }

In another publication using this model~\citep{martin2017human},
a separate error was introduced: the model itself was defined as suggested
in the documentation (using updated parameters
from~\citet{gravel2011demographic}) and inspected
using the \msprime\ debugging tools.
After these initial checks were made, however, the simulation
was performed without passing the parameter of demographic events,
so that the three populations remained separated with low levels of migration and
never merged as expected (Fig~\ref{fig:prs}A),
leading to a vast overestimate of the divergence across human populations.
While the correct model predicts a mean $F_{ST}$ of
$0.05 - 0.10$ across the three population, the simulated model generated $F_{ST}$
ranging between $0.3 - 0.6$, depending on the populations considered.
Overall diversity was also strongly affected: expected heterozygosity was more than
doubled in African populations but just $30-40\%$ the expected
levels in Eurasian populations when compared to expectations from the correct model.

@@

\begin{itemize}
\item Alicia Martin
\item
\end{itemize}

>>>>

\aprcomment{title thoughts: \\
Reducing errors in demographic model design and implementation \\
}

@@

\section{Risk prediction in human populations}

In another publication using this model~\citep{martin2017human},
a separate error was introduced: the model itself was defined as suggested
in the documentation (using updated parameters
from~\citet{gravel2011demographic}) and inspected
using the \msprime\ debugging tools.
After these initial checks were made, however, the simulation
was performed without passing the parameter of demographic events,
so that the three populations remained separated with low levels of migration and
never merged as expected (Fig~\ref{fig:prs}A),
leading to a vast overestimate of the divergence across human populations.
While the correct model predicts a mean $F_{ST}$ of
$0.05 - 0.10$ across the three population, the simulated model generated $F_{ST}$
ranging between $0.3 - 0.6$, depending on the populations considered.
Overall diversity was also strongly affected: expected heterozygosity was more than
doubled in African populations but just $30-40\%$ the expected
levels in Eurasian populations when compared to diversity under the correct model.

@@

\begin{itemize}
\item Alicia Martin
\item stdpopsim as a whole or anyone in particular from that group?
\item others?
\end{itemize}
